---
title: "Package Tutorial"
author: "Bryan Arena"
date: "2022-11-15"
output: html_document
---

# An Introducion to My R Package
My R package is **useful** and will contain _three_ functions. There will be a function useful for removing NA values from a dataset. There will be a function for forming a boxplot for the surveys dataset and another function to form a histogram for the surveys dataset. 

## Installation Instructions

This package will rely heavily on 'tidyverse' 
```{r eval=FALSE, include=TRUE}
install.packages("tidyverse")
```
In order to access my github you will have to install the 'remotes' package, use the library function and use the remotes function to install my github like so:
```{r eval=FALSE, include=TRUE}
install.packages("remotes")
library(remotes)
remotes::install_github("bryanarena/arena_pkg")
```
Now it's time to download my R package:
```{r eval=FALSE, include=TRUE}
install.packages("Final.Data.Analysis.Project")
```
I will now break down how each function was made with their individual code.

**Cleaning the data**
```{r eval=False, include=True}
clean_up <- function(filepath){
  data <- read_csv(filepath)
  clean_up <- data %>% 
    drop_na()
  if (sum(is.na(clean_up)) == 0){
    return(clean_up)
  } else {
    print("NAs still present!")
  }
} 
```
Now you can use the function by inputting the surveys data, for example:
```{r eval=FALSE, include=TRUE}
library(tidyverse)
library(Final.Data.Analysis.Project)
clean_up("Data/surveys.csv")
```
This function is useful for removing all NAs from the dataset
It has been set to show the message "NAs still present"
Since the function works, this message will not appear

**Generating a boxplot**
```{r eval=FALSE, include=TRUE}
jack_box <- function(filepath){
  data <- read_csv(filepath)
  plot <- ggplot(mapping = aes(x = data$species_id, y = data$weight)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
  return(plot)
}
```
Now you can use the function by inputting the surveys data, for example:
```{r eval=FALSE, include=TRUE}
library(tidyverse)
library(Final.Data.Analysis.Project)
jack_box("Data/surveys.csv")
```

**Generating a histogram**
```{r eval=FALSE, include=TRUE}
make_hist <- function(filepath){
  histogram <- hist(surveys$weight)
  return(histogram)
}
```
Now you can use the function by inputting the surveys data, for example:
```{r eval=FALSE, include=TRUE}
library(tidyverse)
library(Final.Data.Analysis.Project)
make_hist("Data/surveys.csv")
```

## Package Conclusion
These functions are designed to make it easier to visualize and interpret specific data. In this case, these functions are made for the surveys dataset. If we find a plot that we feel best represents the variables from the dataset that are used, these functions are great for generating such plots without having to type in the code each time.
